Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2019-09-12 ms/spaceness.tex
msp grid updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Supplementary Figures and Tables}
\beginsupplement

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Supplement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix 1}
\subsection{Comparisons with Alternate Spatial Models}
Stepping-stone models have been extremely useful in population genetics and, when simulated in reverse time, remain much faster than our implementation of continuous-space evolution in forward time. Similarly, the Wright-Malécot models have lead to analytic results that have proved reasonable approximations for estimating neighborhood sizes from empirical data \citep{Rousset1997}. When are these models "good enough"?

First we address a two-dimensional Wright-Malécot model. SLiM includes an implementation of a similar model in recipe 14.1. This model simulates a Wright-Fisher population with discrete generations and fixed total population size. Individuals are initially distributed randomly across the landscape, and each generation

\section{Supplementary Figures and Tables}
\beginsupplement
